% English CV body (Curriculum Vitae)

\begin{center}
  {\Huge \textbf{Jose David Sanabria Aponte}} \\[3pt]
  {\large \textcolor{accent}{\textbf{Senior Backend Developer · Go \& Python · FinTech · AI-Driven Systems}}} \\[4pt]
  \small
  +57 317 503 1582 \;$|$\;
  \href{mailto:josedavidsanabriaaponte@gmail.com}{josedavidsanabriaaponte@gmail.com} \;$|$\;
  \href{https://linkedin.com/in/jdsanabriaa}{linkedin.com/in/jdsanabriaa} \;$|$\;
  \href{https://github.com/jdsanabriaap}{github.com/jdsanabriaap} \;$|$\;
  \href{https://jdsa.dev}{jdsa.dev} \;$|$\;
  Bogotá, Colombia
\end{center}

\vspace{-4pt}

\section*{Professional Summary}

Backend engineer with \textbf{6+ years} building high-throughput payment systems, integration platforms,
and AI-driven automation. At \textbf{Mercado Libre / Mercado Pago}, led LATAM acquirer integrations in Go
— config-driven QR interoperability for \textbf{10+ acquirers} and \textbf{\textasciitilde{}80\%} faster
onboarding via feature flags. Separately, built an organization-wide \textbf{Integration Docs MCP} with a
\textbf{hexagonal-architecture prompt-skill} for all integration teams (web, Markdown, Mermaid docs synced
post-release). Freelance work includes \textbf{Holiday Integrator} (WPF/Playwright B2B scraping), independent
automation projects, and static web with \textbf{OCI + Cloudflare} CI/CD. Personal R\&D: \textbf{VibeWindows}.
Pursuing an \textbf{AI Specialization (UNIR)}.

\section*{Technical Skills}

\begin{itemize}
  \item \textbf{Languages:} Go (Golang), Python, C\# (.NET / WPF), TypeScript, SQL
  \item \textbf{Backend \& Architecture:} Microservices, REST APIs, Hexagonal Architecture, Feature Flags, Config-Driven Integrations, Transactional Flows
  \item \textbf{Data \& AI:} BigQuery, PostgreSQL, MySQL, Computer Vision (OpenCV, MediaPipe, ONNX), Web Scraping (Selenium, Playwright)
  \item \textbf{Observability \& DevOps:} DataDog, Grafana, Git, GitHub Actions, Docker, OCI Object Storage, Cloudflare CDN, Vercel, Azure (AZ-900), Action1 RMM
  \item \textbf{AI Tooling:} Cursor AI — prompt-skills, context-base engineering, architecture-aware agents, Mermaid documentation automation
  \item \textbf{Methodologies:} Agile / Scrum, CI/CD, remote collaboration
\end{itemize}

\section*{Professional Experience}

\jobtitle{Software Developer — Payment Integrations}{Mercado Libre / Mercado Pago}{Feb 2024 – Jan 2026}{Remote · Bogotá}

\begin{itemize}
  \item \textbf{QR Interoperability Platform — Config-Driven Architecture:}
        Refactored QR Interoperable integrations toward a config-driven model (secrets, URLs, contract-based
        adapters), centralizing shared transaction logic — enabling robust onboarding across
        \textbf{10+ active LATAM acquirers}.

  \item \textbf{Feature Flag Architecture — \textasciitilde{}80\% Reduction in Integration Lead Time:}
        Introduced feature flags for \textbf{parallel development and isolated testing} of tokenization
        flows across 10+ acquirers — decoupling release cycles from integration timelines.

  \item \textbf{Integration Docs MCP — Organization-Wide (separate from QR):}
        Built and published a shared \textbf{MCP server} with a \textbf{hexagonal-architecture prompt-skill}
        for \textbf{all Mercado Pago integration teams} (not QR-only). Automates developer documentation
        in \textbf{web and Markdown} with \textbf{Mermaid flow diagrams} — living context for \textbf{AI
        agents and engineers}, refreshed after branch merges and developer-triggered releases.

  \item \textbf{Fiserv Direct Integration (non-QR):}
        Updated messaging contracts between Mercado Pago and Fiserv; validated end-to-end transactional consistency.

  \item \textbf{Transactional Diagnostics via BigQuery:}
        Authored reusable diagnostic playbooks (BigQuery) for Mercado Pago vs.\ acquirer data inconsistencies.

  \item \textbf{Production Observability — DataDog \& Grafana:}
        Expanded monitoring coverage; validated \textbf{zero-regression releases} per acquirer change.
\end{itemize}

\vspace{4pt}

\jobtitle{Automation \& AI Developer (Contractor)}{Holiday Experiences S.A.S.}{2020 – Present}{Bogotá}

\textit{Independent projects for the same client — not a single monolithic product.}

\begin{itemize}
  \item \textbf{Holiday Integrator} (\texttt{HolidayScraperApp}) — \textbf{C\# / WPF / Playwright:}
        Desktop app for parallel B2B tourism portal scraping (BedsOnline, HotelDo, TravelC, etc.),
        Union-Find offer aggregation, mosaic/list/map UI, and reservation handoff with visible browser sessions.

  \item \textbf{IFX \& Zadarma Call Compliance — Python:}
        Pipeline replacing hours of daily manual call-recording handling — full legal compliance with zero human intervention.

  \item \textbf{Cross-Border Contract Sync (Colombia \textrightarrow{} US) — Selenium + OpenCV:}
        Extracts contract data locally and submits to the US Data Principal platform via CV-driven UI automation.

  \item \textbf{Enterprise IT \& RMM:}
        Deployed and manages \textbf{Action1 RMM} for centralized patching and endpoint security.
\end{itemize}

\vspace{4pt}

\jobtitle{Web Developer (Contractor)}{Club House Petlandia}{Jan 2025}{Remote}

\begin{itemize}
  \item Static multi-page landing (HTML/CSS/JS) for pet boarding in Madrid, CO — WhatsApp lead conversion and local SEO.
  \item \textbf{CI/CD:} GitHub Actions \textrightarrow{} OCI Object Storage \textrightarrow{} Cloudflare CDN purge on push to \texttt{master}.
  \item Production: \href{https://petlandiaclubhouse.com}{petlandiaclubhouse.com}
\end{itemize}

\section*{Personal Projects}

\begin{itemize}
  \item \textbf{VibeWindows} (v0.2.2) — WPF/.NET 8 hand-gesture cursor control: CaptureBroker \textrightarrow{}
        VisionSession \textrightarrow{} ONNX or Python TCP vision engines \textrightarrow{} multi-monitor virtual desktop;
        injection safety OFF by default. MVP \textasciitilde{}95\% complete.
\end{itemize}

\section*{AI Tooling \& Engineering Practices}

\textbf{1+ year} of production \textbf{Cursor AI} — from instruction prompts to \textbf{prompt-skills},
structured context bases, and hexagonal-architecture-aware documentation pipelines (web, Markdown, Mermaid).
Applied to integration onboarding, concurrent Go services, and large-volume data diagnostics.

\section*{Education}

\noindent\textbf{\color{dark}Specialization in Artificial Intelligence} \hfill \textit{\color{light}Nov 2025 – Present} \\
\textbf{\color{accent}International University of La Rioja (UNIR)} \hfill \textcolor{light}{Remote}

\vspace{5pt}

\noindent\textbf{\color{dark}B.S. in Systems Engineering} \hfill \textit{\color{light}2017 – 2024} \\
\textbf{\color{accent}Universidad Distrital Francisco José de Caldas} \hfill \textcolor{light}{Bogotá}

\section*{Certifications}

\begin{itemize}
  \item \textbf{AZ-900} — Microsoft Certified: Azure Fundamentals
  \item \textbf{SFPC} — Scrum Foundation Professional Certificate
\end{itemize}
